Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-09-03 Papers/ms.tex
Truth values for easy data

\section{{\revisions``Easy''} Simulated Data}
To demonstrate the method, we generated a simulated dataset {\revisions where
the lens was an SIE$+\gamma$ profile with a single additional substructure}.
The image is shown in Figure~\ref{fig:image1}, and
consists of 100 $\times$ 100 pixels. The point spread function (PSF) was compact and was
defined on a 5 $\times$ 5 grid. The data was created by firing only one ray
per pixel, and the inference was also carried out under the same level of
approximation. Since the model assumptions are all correct for this image, the
demonstration here is purely to illustrate the computational tractability of
the problem, and the kind of outputs the method can produce.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{image1.pdf}
\caption{A simulated image of a simple ``galaxy'' lensed by an SIE+$\gamma$
lens in the center of the image (which does not contribute any flux), plus a
single substructure close to the top left image.
The image was blurred by a PSF and had some noise added.\label{fig:image1}}
\end{center}
\end{figure}

>>>>

\section{{\revisions``Easy''} Simulated Data}
To demonstrate the method, we generated a simulated dataset {\revisions where
the lens was an SIE$+\gamma$ profile with a single additional substructure}.
The image is shown in Figure~\ref{fig:image1}, and
consists of 100 $\times$ 100 pixels. The point spread function (PSF) was compact and was
defined on a 5 $\times$ 5 grid. The data was created by firing only one ray
per pixel, and the inference was also carried out under the same level of
approximation. Since the model assumptions are all correct for this image, the
demonstration here is purely to illustrate the computational tractability of
the problem, and the kind of outputs the method can produce.
{\revisions
The SIE$+\gamma$ parameters were
$\{b, q, x_c^{\rm SIE}, y_c^{\rm SIE}, \theta, \gamma, \theta_\gamma\}
= \{5.25, 0.323, 0.191, -0.341, 0.833, 0.0322, 0.497\}$, where the length
units in the image plane are arbitrary, and rotation angles are measured in
radians. The single substructure is located at $(-2.57, 2.20)$, close to the
upper left image. Its mass is 2.50 units, using the convention where the
critical density is 1. For comparison, the SIE mass within its critical
ellipse is $\pi b^2 = 86.6$ units.
}

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{image1.pdf}
\caption{A simulated image of a simple ``galaxy'' lensed by an SIE+$\gamma$
lens close to the center of the image (which does not contribute any flux), plus a
single substructure close to the top left image.
The image was blurred by a PSF and had some noise added.
In an arbitrary system of units, this image extends from -8 to 8 in the
$x$ and $y$ directions.\label{fig:image1}}
\end{center}
\end{figure}
